### 2019-03-18 README.Rmd
Hide citation code in README
Add reference to rcites/Speciesplus

@@

```{r, results = "asis"}
print(citation("citesdb"), style = "textVersion")
```

>>>>

### Related work

The [**rcites**](https://github.com/ropensci/rcites) package provides
access to the Speciesplus/CITES Checklist API, which includes metadata about
species and their protected status through time.

@@

```{r, results = "asis", echo = FALSE}
print(citation("citesdb"), style = "textVersion")
```
